---
title: "igraph_practice_KA.Rmd"
output: html_document
---

Goal: The purpose of this R script is to practice using the igraph package. I learned about this technique from the ASM meetings in the summer of 2019. Noé de la Sancha used this package to predict a forest network with graph theory. 
•	Graph theory- represent forest patches with nodes and connect nodes with lines called edges
o	Nodes connected to a bunch of other nodes is called an edge
o	Try to create a network via nodes 
o	Certain forest patches are essential points in the network (cutpoints)

Sancha said he is not yet sure how graph theory influences connectivity, but this could be helpful when determining the best path for movement within the A2A corridor. 

Some important measurements include:
o	Coalescence distance- minimum distance that organism would have to travel in order to get through the network 
o	Average number of links
o	Stepping stones
o	Hubs
o	Cutpoints

•	Focal area of the nodes is valuable and will change patterns at regional scale
•	Small forest remnants are important in maintaining connectivity
•	Distance between nodes beyond dispersal capacity of many animals- need to account for target species 



```{r}
rm(list = ls())
library(dplyr)
library(readr)
library(ggplot2)
install.packages(igraph)
library(igraph)
library(maptools)
```

```{r}
## A simple example with a couple of actors
## The typical case is that these tables are read in from files....
actors <- data.frame(name=c("Alice", "Bob", "Cecil", "David",
                            "Esmeralda"),
                     age=c(48,33,45,34,21),
                     gender=c("F","M","F","M","F"))
relations <- data.frame(from=c("Bob", "Cecil", "Cecil", "David",
                               "David", "Esmeralda"),
                        to=c("Alice", "Bob", "Alice", "Alice", "Bob", "Alice"),
                        same.dept=c(FALSE,FALSE,TRUE,FALSE,FALSE,TRUE),
                        friendship=c(4,5,5,2,1,1), advice=c(4,5,5,4,2,3))
g <- graph_from_data_frame(relations, directed=TRUE, vertices=actors)
print(g, e=TRUE, v=TRUE)

V(g) #shows the number of vertices, the output from the 'name' row
E(g) #shows the possible connections within the network 

## The opposite operation
as_data_frame(g, what="vertices")
as_data_frame(g, what="edges")


plot.igraph(g)
#This displays a really cool graph of the network created from these two data frames!!!

tkplot(g)
#This displays an interactive graph that you can manipulate

rglplot(g)
#This displays a 3D graph that can be moved around in the space
```


Playing around with functions
```{r}
# Create new vertex attribute called 'gender'
g <- set_vertex_attr(g, "gender", value = genders)

# Create new vertex attribute called 'age'
g <- set_vertex_attr(g, "age", value = 10)
```



Need to create a data frame showing the connections of the forest fragments within the A2A corridor.
```{r}
library(readr)
DF <- read_csv("~/Dropbox/Zooniverse_work/Kate/igraph/igraph_practice_KA.csv")
```


