---
title: "Finding differences between times on photos"
output: html_notebook
---
Set up the workspace
```{r}
rm(list = ls())
library(dplyr)
```

Need to be able to determine the differences in times between files

First identify the files in the folder
```{r}
filepath<- ("/Users/ebar/Dropbox/R/Zooniverse_work/Small batch")
#filepath<-("/Users/ebar/Dropbox/R/Zooniverse_work/Small batch") #from laptop
#filepath<-("/Volumes/External Drive/Dropbox/R/Zooniverse_work/Small batch") #from mac pro

files<-list.files(filepath)
```
Now obtain the metadata for the images
Let's see if we can do this by calling exiftool within R

```{r}
#library(exiftoolr)
#exif_call(args = "-csv . > collectionprofile1.csv",path =  "/Volumes/External Drive/Dropbox/R/Zooniverse_work/Small batch") #this may be very slow - may be better to create the .csv file using the command line and then just import it. For 36 images, this took about 1 second on the command line and it has been churning away for a long time (> 10 min now) on R
#now read in csv
library(readr)
library(readr)
DF <- read.csv("test.csv")#change name of DF to Meta
Meta<-DF


#great
```

Now that we have the metadata, we can see that the DateTimeOriginal column came in as a factor.  Let's change it with lubridate

```{r}
library(lubridate)
Meta$DateTimeOriginal<-ymd_hms(Meta$DateTimeOriginal)
Meta1<-Meta[order(Meta$DateTimeOriginal),]
```
Now see if we can calculate the differences

```{r}
MyDiffs<-diff(Meta1$DateTimeOriginal)
MyDiffs<-as.numeric(MyDiffs)

#now see if we can convert seconds to minutes, minutes to hours, hours to days
MyDiffs_Minutes<-MyDiffs/60
MyDiffs_Hours<-MyDiffs_Minutes/60
MyDiffs_Days<-MyDiffs_Hours/24

MyDiffs_Minutes
```
This seems to be working!  Now let's see if we can assign images to events using this logic

```{r}
thresh<-60 #set a threshold for number of seconds between events
ev<-vector()
L <- length(Meta1$DateTimeOriginal)

for(i in 1:length(Meta1$DateTimeOriginal)){
     interval<-diff(Meta1$DateTimeOriginal)
     #now convert to minutes
     
     ev<-1; res<-numeric() #created new var called ev and set to 1, created empty numeric vector called res
   }
cond<- interval > thresh #sets condition for assigning to a new event where minutes corresponds to thresh
   
   for(i in 1:(L-1)){
      if(!cond[i]) ev<-ev else ev<-ev+1
      res<-c(res,ev)
   }
  MyResult<-c(1,res)
#I think this works!  res has the event we need
```
Now append to csv to examine
```{R}
Meta1$Event<-MyResult


#Kate and Erika worked through this on 2-5-19 and think it is now working and assigning to proper groups because we ordered the pictures in line 37
```
Now export Meta1 for building the manifest

```{r}
write.csv(Meta1, "Images_by_event.csv")
```



  
