---
title: "Chapter 5 Zooniverse Modifications"
output: html_notebook
---

The goal of this R Notebook is to reorder the data frame we get from Zooniverse to match the format from Wild.ID. This will allow us to use the functions from Chapter 5 to calculate naïve occupancy, RAI, and species accumulation.

Load necessary packages and clear the environment
```{r}
rm(list=ls())

library(dplyr)
library(tidyverse)
library(tidyr)
library(readr)
library(lubridate)
library(chron) #works with chronological objects like dates and times
library(reshape) #restructures and aggregates data in a flexible way
library(vegan) #ecological analysis
library(plotrix) #visualize circular data
library(ggplot2) #producing graphics
library(maptools) #produce maps using GIS layers
```

Now load the latest version of the data frame. This was modified from a previous R Notebook called 'cleaning_dataKA.Rmd'. The file is called 'ImageDates2.csv'
```{r}
DF <- read.csv("~/Dropbox/Zooniverse_work/Gus.csv")
```

There are unnecessary columns in this data frame, so let's remove those. 
```{r}
DF1<-subset(DF, select= c("Image1","DateTimeOriginal","Camera_Trap_Days", "Date_Out", "Date_Checked","choice"))
```

Source functions from Wild.ID chapters in console
```{r}
source("TEAM library 1.7.R")
```

Get DF1 to match format for 'data' in the Wild.ID chapter
```{r}
#Change column headings 
names(DF1)<-c("Sampling.Unit.Name", "td.photo", "ndays", "Start.Date", "End.Date", "bin")
```

Let's try replicating the td.photo column twice and then take away date in one column and time in the other.
```{r}
n<-2
DF2<-cbind(DF1, replicate(n,DF1$td.photo))

```

Correct Dates in DF1
```{r}
DF2$Start.Date<- ymd(DF2$Start.Date)
DF2$End.Date<- ymd(DF2$End.Date)
DF2$td.photo<- ymd_hms(DF2$td.photo)
```

Change column heading to get 'Photo.Date' and 'Photo.Time'
```{r}
names(DF2)<-c("Sampling.Unit.Name", "td.photo", "ndays", "Start.Date", "End.Date", "bin", "Photo.Date", "Photo.Time")
```

Get rid of dates from 'Photo.Time' and times from 'Photo.Date'
```{r}
#Gets rid of time from 'Photo.Date'
DF2$Photo.Date<- ymd_hms(DF2$Photo.Date)
DF2$Photo.Date<-as.Date(DF2$Photo.Date, format = "%y/%m/%d")

#Gets rid of date from 'Photo.Time'
DF2$Photo.Time<- ymd_hms(DF2$Photo.Time)
DF2$Photo.Time<- strftime(DF2$Photo.Time, format = "%H:%M:%S")
#Puts in time that is 5 hours behind the td.photo time. Perhaps need to account for time zone. 
```


Add sampling year column because Wild.ID requires it
```{r}
list<- DF2
Sampling.Event<- rep("2019.01", length(DF2$Sampling.Unit.Name))
DF3<-cbind(list,Sampling.Event)
```

Write csv file to keep as standard data frame to use on other calculations. This will make it easier when I want to quickly recalculate values. 
```{r}
write.csv(DF3, file = "masterDF.csv")
```


Calculate events per species and camera trap
Run threshold for 1 day (thresh=1440)
```{r}
#Need to load the plyr function for this to work. Was getting an error before that said all arguments must be named.
library(plyr)
events_dd<- event.sp(dtaframe=DF3, year= 2019.01, thresh=1440)

#Problem with one td.photo date and Start.Date. First photo captured before deployment date. May need to look into how I merged the image dates. Could also be a problem with the camera. 
```


Write Summary Table
```{r}
events_dd_sepcies<- colSums(events_dd)
events_dd_sepcies
```




Calculate Species Activity
```{r}
activity_24h<- events.hours(DF3)

```


Calculate Jaccard Index
This currently does not work. Had to calculate by hand in excel.
```{r}
Jaccard <- function (x, y) {
    M.11 = sum(x == 1 & y == 1)
    M.10 = sum(x == 1 & y == 0)
    M.01 = sum(x == 0 & y == 1)
    return (M.11 / (M.11 + M.10 + M.01))
}
 
input.variables <- data.frame(Q6_01, Q6_02, Q6_03, Q6_04, Q6_05, Q6_06, Q6_07, Q6_08, Q6_09)
 
m = matrix(data = NA, nrow = length(input.variables), ncol = length(input.variables))
for (r in 1:length(input.variables)) {
    for (c in 1:length(input.variables)) {
        if (c == r) {
            m[r,c] = 1
        } else if (c > r) {
            m[r,c] = Jaccard(input.variables[,r], input.variables[,c])
        }
    }
}
 
variable.names = sapply(input.variables, attr, "label")
colnames(m) = variable.names
rownames(m) = variable.names   
         
jaccards = m
```

Calculate camera trap days
```{r}
sum(DF3$ndays)

CamDays<- DF %>% group_by(Camera) %>% summarise(
     n_camdays = unique(Camera_Trap_Days)
)
```

