---
title: "Chapter 5 Zooniverse Modifications"
output: html_notebook
---

The goal of this R Notebook is to reorder the data frame we get from Zooniverse to match the format from Wild.ID. This will allow us to use the functions from Chapter 5 to calculate naïve occupancy, RAI, and species accumulation.

Load necessary packages and clear the environment
```{r}
rm(list=ls())

library(dplyr)
library(tidyr)
library(readr)
library(lubridate)
library(chron) #works with chronological objects like dates and times
library(reshape) #restructures and aggregates data in a flexible way
library(vegan) #ecological analysis
library(plotrix) #visualize circular data
library(ggplot2) #producing graphics
library(maptools) #produce maps using GIS layers
```

Now load the latest version of the data frame. This was modified from a previous R Notebook called 'cleaning_dataKA.Rmd'. The file is called 'ImageDates2.csv'
```{r}
DF <- read.csv("~/Dropbox/Zooniverse_work/Camera_Trapping_Ch5_Work/ImageDates2.csv")
```

There are unnecessary columns in this data frame, so let's remove those. 
```{r}
DF1<-subset(DF, select= c("Image1","DateTimeOriginal","Camera_Trap_Days", "Date_Out", "Date_Checked","choice"))
```

Source functions from Wild.ID chapters in console
```{r}
source("TEAM library 1.7.R")
```

Get DF1 to match format for 'data' in the Wild.ID chapter
```{r}
#Change column headings 
names(DF1)<-c("Sampling.Unit.Name", "td.photo", "ndays", "Start.Date", "End.Date", "bin")
```

Let's try replicating the td.photo column twice and then take away date in one column and time in the other.
```{r}
n<-2
DF2<-cbind(DF1, replicate(n,DF1$td.photo))

```

Correct Dates in DF1
```{r}
DF2$Start.Date<- ymd(DF2$Start.Date)
DF2$End.Date<- ymd(DF2$End.Date)
DF2$td.photo<- mdy_hm(DF2$td.photo)
```

Change column heading to get 'Photo.Date' and 'Photo.Time'
```{r}
names(DF2)<-c("Sampling.Unit.Name", "td.photo", "ndays", "Start.Date", "End.Date", "bin", "Photo.Date", "Photo.Time")
```

Get rid of dates from 'Photo.Time' and times from 'Photo.Date'
```{r}
DF2$Photo.Date<-separate(DF2, Photo.Date, sep = "[^[1/1/19 10:52:alnum:1/1/19]]+", remove = TRUE, convert = FALSE, extra = "drop")
```


Add sampling year column because Wild.ID requires it
```{r}
list<- DF2
Sampling.Event<- rep("2019.01", length(list))
DF3<-cbind(list,Sampling.Event)
```


Calculate events per species and camera trap
Run threshold for 1 day (thresh=1440)
```{r}
events_dd<- event.sp(dtaframe=DF2, year= 2019.01, thresh=1440)

#Need to split td.photo into Photo.Date and Photo.Time columns as well to satisfy requirements for event.sp function. 

#Problem with td.photo first few dates and Start.Date. First photo captured before deployment date. May need to look into how I merged the image dates. Could also be a problem with the camera. 
```






