---
title: "Image Pre-processing 1: Assign images to events"
output: html_notebook
---
##Introduction
This is the R code needed to use the metadata from a folder of images to compare the image time stamps and group images into their respective "events."

An event is a set of pictures taken within a time threshold.  We set our cameras to take up to 3 pictures in a bout, and set them with a 1 minute delay before they can take more pictures, so we can use 1 minute as our threshold.

###Before you begin

In order to run this code, you will need to have the following in place:

* A folder with a set of images (and only images) in it.
* A csv file made using *exiftool* that has date/time metadata from all of the photos in the folder


###Step 1
Set up the workspace
```{r}
rm(list = ls())
library(dplyr)
library(readr)
library(lubridate)
```
###Step 2

First identify the folder containing the images and create a variable that is the list of file names. 

```{r}
#filepath<-(path to hard drive)
filepath<- ("/Users/ebar/Dropbox/R/Zooniverse_work/Round1")#may have to redirect to wherever the pictures are stored.


#filepath<-("/Volumes/External Drive/Dropbox/R/Zooniverse_work/Small batch") #from mac pro

files<-list.files(filepath) #creates variable files as list of filenames
```
###Step 3 
Now we need to pull in the image metadata.  It was generated and saved as a .csv outside of R using a tool called *exiftool* that is run from the command line.  We should see if we can get *exiftool* installed on the HPC. It works to run exiftool within R (library(exiftool)), but it is VERY VERY SLOW. 

```{r}

#library(readr) if not called at top of code
Meta <- read.csv("/Users/ebar/Dropbox/R/Zooniverse_work/Round1/Round1.csv") #obvioulsly, put correct file name here

files<-Meta$FileName
files<-as.character(files)
```

###Step 4
Now that we have the metadata, we can see that the DateTimeOriginal column came in as a factor.  Let's change it with lubridate.  Note that then a very important step is to ORDER the data frame in terms of date/time.  If you fail to order the data frame, when you compare dates/times you will get incorrect output.

```{r}
#library(lubridate)if not called at top of code 
Meta$DateTimeOriginal<-ymd_hms(Meta$DateTimeOriginal)
Meta<-Meta[order(Meta$DateTimeOriginal),]#THIS IS KEY
```
Now see if we can calculate the time differences among the photos

```{r}
MyDiffs<-diff(Round1_Batch1$DateTimeOriginal)#returns what looks like an empty variable in the environment window
MyDiffs<-as.numeric(MyDiffs) #now it shows up as numeric data

#Optional: now see if we can convert seconds to minutes, minutes to hours, hours to days
#MyDiffs_Minutes<-MyDiffs/60
#MyDiffs_Hours<-MyDiffs_Minutes/60
#MyDiffs_Days<-MyDiffs_Hours/24

#MyDiffs_Minutes
```
Problem: Some of the images have the incorrect Date/Time due to camera resetting to 2013.  We are going to extract those and make them Round1_Batch2.csv and get all others for Round1_Batch1.csv so we can get something to zooniverse.
```{r}
Round1_Batch1<-filter(Round1_Batch1, DateTimeOriginal == "2013-01-01")

Round1_Batch1$DateTimeOriginal<-as_date(Round1_Batch1$DateTimeOriginal)

Dump<-which(Round1_Batch1$DateTimeOriginal == "2013-01-01")
```

Monkeying around trying to extract by date
```{r}
Meta$Sort<-Meta$DateTimeOriginal
Meta$Sort<-as.character(Meta$Sort)
Meta$Sort<-as.factor(Meta$Sort)
levels(Meta$Sort)
Round1_Batch2<-filter(Meta, Sort <"2018-01-12 12:34:51")
Round1_Batch1<-filter(Meta, Sort > "2017-12-31 18:16:49")
length(Round1_Batch1$Sort)+length(Round1_Batch2$Sort)
write.csv(Round1_Batch1, file = "/Users/ebar/Dropbox/R/Zooniverse_work/Round1/R1B1.csv")
write.csv(Round1_Batch2, file ="/Users/ebar/Dropbox/R/Zooniverse_work/Round1/R1B2.csv" )
filepath
```




###Step 5 
This seems to be working!  Now let's see if we can assign images to events using this logic.  We will need to set the time threshold (default is 1 minute).

```{r}
thresh<-60 #set a threshold for number of seconds between events
ev<-vector()
L <- length(Round1_Batch1$DateTimeOriginal)

for(i in 1:length(Round1_Batch1$DateTimeOriginal)){
     interval<-diff(Round1_Batch1$DateTimeOriginal)
     #now convert to minutes
     
     ev<-1; Event_num<-numeric() #created new var called ev and set to 1, created empty numeric vector called Event_num. Event_num will store the assigned event for each image
   }
cond<- interval > thresh #sets condition for assigning to a new event where minutes corresponds to thresh
   
   for(i in 1:(L-1)){
      if(!cond[i]) ev<-ev else ev<-ev+1
      Event_num<-c(Event_num,ev)
   }
  Event<-c(1,Event_num)

```
Now append the Event to the data frame csv to capture the event assignment for each image.
```{R}
Round1_Batch1$Event<-Event

test<-tail(Round1_Batch1, 60)
```
###Step 6
Now export Meta for use in assigning images to "image numbers" in the zooniverse manifest style
```{r}
write.csv(Round1_Batch1, "/Users/ebar/Dropbox/R/Zooniverse_work/Round1/Images_by_event.csv")
```



  
