---
title: "Shannon and Simpson’s indices"
author: "Erika"
date: "4/25/2019"
output: html_document
---
We'd like to cacluate Shannon and Simpon indices for the winter 2018-2019 camera trap data.

Set up workspace
```{r setup, include=FALSE}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(readr)
```

Now load "raw" camera trap data
```{r}
DF <- read_csv("~/Dropbox/Zooniverse_work/Kate/Gus.csv")
```
Now get rid of the "NOTHINGHERE" and "SOMETHINGHERE" since they provide no species information.

```{r}
dump<-which(DF$choice == "NOTHINGHERE" | DF$choice == "SOMETHINGHERE" | DF$choice == "HUMAN")

#now dump
DF<-DF[-dump,]
```
Next, we need to create a matrix or df of sites on rows and species on columns with cells equal to # of events.

Summarize by species and forest and return # of events.

```{r}
diversity<-DF %>% group_by(ForestName, choice) %>% summarize(
	NumEvents = length(Camera)
)
```
Now we need to format diversity for vegan.

Use tidyr
```{r}
library(tidyr)
divVegan<- spread(diversity, choice, NumEvents)
```

Now, for vegan, replace NA's with zero and also delete the first column.

```{r}
#replace NAs with zeros
divVegan[is.na(divVegan)] <- 0
#dump first column
vegReady<-divVegan[,-1]
```

Run the diversity function for shannon diveristy index (increases as diversity increases)
```{r}
div_shan<-diversity(vegReady, index = "shannon")
div_shan
```

Do the same for the simpson's index (similarity index- take 1-S to find diversity index). Measurement of probability that any two randomly selected individuals from infinitely large community will belong to same species.
```{r}
div_simp<- diversity(vegReady, index = "simpson")
div_simp
```

Plot the two indices, bar graph of all forest sites. Box plot for two forest types. 

Create DF with forest name in one column and diversity in another. 
```{r}
library(tidyr)
Forest<- unique(divVegan$ForestName)
shanDiv<- as.data.frame(cbind(div_shan, Forest))

```

Plot bar graph of Shannon Index Diversity
```{r}
shanDiv$Type<- as.factor(c("D","P","D","D","P","P"))
shanDiv$div_shan<- as.numeric(as.character(shanDiv$div_shan))
ggplot(shanDiv, aes(x= Forest, y = div_shan, group = Type, color = Type)) + 
     geom_col(position= "dodge")+ 
     xlab("Forest") +
     ylab("Shannon Diversity Index")
     

ggsave("Shannon_Diversity_Index.jpg", device= "jpg")
```

Do the same for Simpson's Index
```{r}
simpDiv<-as.data.frame(cbind(div_simp, Forest))
simpDiv$Type<- as.factor(c("D","P","D","D","P","P"))

simpDiv$div_simp<- as.numeric(as.character(simpDiv$div_simp))
ggplot(simpDiv, aes(x= Forest, y = div_simp, group = Type, color = Type)) + 
     geom_col(position= "dodge") +
     xlab("Forest") +
     ylab("Simpson's Diversity Index")

ggsave("Simpson's_Diversity_Index.jpg", device = "jpg")
```

Calculations to find the standard deviation and mean for species richness in deciduous study sites. 
```{r}
specRich <- read_csv("~/Dropbox/Zooniverse_work/Kate/Species Richness Test.csv")

specRich1<- specRich %>% summarise(
     meanRich = mean(SR),
     sd = sd(SR)
)
```

