---
title: "First pass at occupancy modeling with RPresence and Unmarked"
output: html_notebook
---

##Introduction
Working on occupancy modeling from camera trap data.


## Step 1.
Prep the workspace and load the data
```{r}
rm(list=ls())
library(tidyr)
library(dplyr)
library(ggplot2)
library(unmarked)
#install.packages("/Volumes/External Drive/Dropbox/R/Packages/RPresence_2.12.29.tar.gz", repos = NULL, type = "source") #to download the RPresence package
#library(RPresence)
library(readr)

#DF <- read_csv("/Volumes/External Drive/Dropbox/R/Zooniverse_work/Fisher_Occupancy/Fisher_occupancy_datasheet.csv")
DF <- read_csv("/Users/ebar/Dropbox/R/Zooniverse_work/Fisher_Occupancy/Fisher_occupancy_datasheet.csv")

str(DF)
glimpse(DF)
```
Clean up a bit by deleting X2 column

```{r}
DF<-DF[,-2]
```
These data are structured with camera number as the first column, and camera trap day as the next (109!) series of columns.  Each value in a cell is a 0 (not detected), 1(present, i.e. detected) or NA (camera was not out at that time)

The remaining columns are the covariates that may help to explain species presence or absence. Presence indicates the presence of any of a set of mesocarnivore species (raccoon, bobcat, skunk, coyote, fox, fisher, weasel etc.)

##Step 2.


```{r}
Occ.DF<-DF[,2:110]
```

In the case of our data, occ.data corresponds to the y matrix of an unmarked frame, and the df of site covarites is the remainder of DF.

Put the site covariates into a DF, then combine with occupancy data and pass to unmarkedFrameOccu object.  

```{r}
OccCovariates<-DF[,111:138]
OurData<-unmarkedFrameOccu(Occ.DF, siteCovs = OccCovariates)
summary(OurData)

```


```{r}
plot(OurData, panels = 4)
mod1<-occu(~ 1 ~1, OurData)
mod1
```
Now back transform
```{r}
#now get the estimates for detection
backTransform(mod1['det'])
```

