---
title: "Image Pre-processing 1: Assign images to events"
output: html_notebook
---
##Introduction
This is the R code needed to use the metadata from a folder of images to compare the image time stamps and group images into their respective "events."

An event is a set of pictures taken within a time threshold.  We set our cameras to take up to 3 pictures in a bout, and set them with a 1 minute delay before they can take more pictures, so we can use 1 minute as our threshold.

###Before you begin

In order to run this code, you will need to have the following in place:

* A folder with a set of images (and only images) in it.
* A csv file made using *exiftool* that has date/time metadata from all of the photos in the folder


###Step 1
Set up the workspace
```{r}
rm(list = ls())
library(dplyr)
library(readr)
library(lubridate)
```
###Step 2
Now we need to pull in the image metadata.  It was generated and saved as a .csv outside of R using a tool called *exiftool* that is run from the command line.  We should see if we can get *exiftool* installed on the HPC. It works to run exiftool within R (library(exiftool)), but it is VERY VERY SLOW. 

```{r}
#library(readr) if not called at top of code
Meta <- read.csv("/Volumes/External Drive/Dropbox/R/Zooniverse_work/Kate/R1B2.csv") 
#obvioulsly, put correct file name here
#Meta<-read.csv("/Users/keandy16/Dropbox/Zooniverse_work/Kate/R1B2.csv")
```

###Step 3
Now that we have the metadata, we can see that the DateTimeOriginal column came in as a factor.  Let's change it with lubridate.  Note that then a very important step is to ORDER the data frame in terms of date/time.  If you fail to order the data frame, when you compare dates/times you will get incorrect output.

```{r}
#library(lubridate)if not called at top of code 
Meta$DateTimeOriginal<-ymd_hms(Meta$DateTimeOriginal)
#Meta<-Meta[order(Meta$DateTimeOriginal, Meta$FileName),]#THIS IS KEY
```
###Step 4
Need to filter by camera.  First make new camera number variable.

```{r}
#first make Fielname a chr var
Meta$FileName<-as.character(Meta$FileName)
Meta$cam_num<-substr(Meta$FileName, 1, 5) #grabs the first through fifth characters from the file name
cams<-unique(Meta$cam_num)
```

Next, create a loop to filter and process by camera

```{r}
#set some initial parameters
maxEvent<-1
thresh<-5

for (i in 1:length(cams)){
  #subset the DF by camera
  tempDF<-filter(Meta, cam_num == cams[i])
  tempDF
  tempDF<-tempDF[order(tempDF$FileName),] #make sure in order of filename and not time
  #now we have the subset; need to process using old code
  
  #calculate time differences for tempDF
  MyDiffs<-diff(tempDF$DateTimeOriginal)#returns what looks like an empty variable in the environment window
  MyDiffs<-as.numeric(MyDiffs) #now it shows up as numeric data
  #Now let's see if we can assign images to events using this logic.  We will need to set the time threshold    to something very short since dates/times are messed up (camera reset). Try 5 seconds.
  
  #thresh<-5 #set a threshold for number of seconds between events
  ev<-vector()
  L<-length(tempDF$DateTimeOriginal)
  
    for(x in 1:L){
      interval<-diff(tempDF$DateTimeOriginal)
      ev<-1; Event_num<-numeric() 
      #created new var called ev and set to 1, created empty numeric vector called Event_num. 
      #Event_num will store the assigned event for each image
    }       
  cond<- interval > thresh #sets condition for assigning to a new event where minutes corresponds to thresh
    if (i == 1) ev<-1 else ev<-maxEvent    
    
    for(z in 1:(L-1)){#this is where the problem is; resets event numbers
      if(!cond[z]) ev<-ev else ev<-ev+1
      Event_num<-c(Event_num,ev) 
    }
    Event<-c(maxEvent,Event_num)
           
    tempDF$Event<-Event
    #newDF<-tempDF
    #testing saving each DF
    #name<-paste0("NewDF", i)
    
    if (i == 1) {
      newDF <- tempDF} else {
      newDF<- rbind(newDF, tempDF)
    }
    maxEvent<-(max(newDF$Event)+1)
}
   #this is working, but we need it to continue numbering the events consecutively between cameras
     


  #write.csv(tempDF,"~/Dropbox/Zooniverse_work/Kate/Images_by_event.csv")

#last(tempDF$Event)

```










```{r}
MyDiffs<-diff(Meta$DateTimeOriginal)#returns what looks like an empty variable in the environment window
MyDiffs<-as.numeric(MyDiffs) #now it shows up as numeric data

#Optional: now see if we can convert seconds to minutes, minutes to hours, hours to days
#MyDiffs_Minutes<-MyDiffs/60
#MyDiffs_Hours<-MyDiffs_Minutes/60
#MyDiffs_Days<-MyDiffs_Hours/24

#MyDiffs_Minutes
```
###Step 5 
This seems to be working!  

```{r}
thresh<-60 #set a threshold for number of seconds between events
ev<-vector()
L <- length(Meta$DateTimeOriginal)

for(i in 1:length(Meta$DateTimeOriginal)){
     interval<-diff(Meta$DateTimeOriginal)
     #now convert to minutes
     
     ev<-1; Event_num<-numeric() #created new var called ev and set to 1, created empty numeric vector called Event_num. Event_num will store the assigned event for each image
   
cond<- interval > thresh #sets condition for assigning to a new event where minutes corresponds to thresh
   
   for(i in 1:(L-1)){
      if(!cond[i]) ev<-ev else ev<-ev+1
      Event_num<-c(Event_num,ev)
  }
  Event<-c(1,Event_num)
  

```
Now append the Event to the data frame csv to capture the event assignment for each image.
```{R}
Meta$Event<-Event
```
###Step 6
Now export Meta for use in assigning images to "image numbers" in the zooniverse manifest style
```{r}
write.csv(Meta, "Images_by_event.csv")
```

###NOTE
This does not work because it sorts by date and time, not by date and time per forest.

  