---
title: "Shannon and Simpson’s indices"
author: "Erika"
date: "4/25/2019"
output: html_document
---
We'd like to cacluate Shannon and Simpon indices for the winter 2018-2019 camera trap data.

Set up workspace
```{r setup, include=FALSE}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(readr)
```

Now load "raw" camera trap data
```{r}
DF <- read_csv("~/Dropbox/R/Zooniverse_work/Gus.csv")
```
Now get rid of the "NOTHINGHERE" and "SOMETHINGHERE" since they provide no species information.

```{r}
dump<-which(DF$choice == "NOTHINGHERE" | DF$choice == "SOMETHINGHERE" | DF$choice == "HUMAN")

#now dump
DF<-DF[-dump,]
```
Next, we need to create a matrix or df of sites on rows and species on columns with cells equal to # of events.

Summarize by species and forest and return # of events.

```{r}
diversity<-DF %>% group_by(ForestName, choice) %>% summarize(
	NumEvents = length(Camera)
)
```
Now we need to format diversity for vegan.

Use tidyr
```{r}
library(tidyr)
divVegan<- spread(diversity, choice, NumEvents)
```

Now, for vegan, replace NA's with zero and also delete the first column.

```{r}
#replace NAs with zeros
divVegan[is.na(divVegan)] <- 0
#dump first column
vegReady<-divVegan[,-1]
```


