---
title: "Image Pre-processing 1: Assign images to events"
output: html_notebook
---

##This code does not work. See "Extract_Image_Metadata_Date_Issues.Rmd" in the "UseThisCode" folder for the correct version.


##Introduction
This is the R code needed to use the metadata from a folder of images to compare the image time stamps and group images into their respective "events."

An event is a set of pictures taken within a time threshold.  We set our cameras to take up to 3 pictures in a bout, and set them with a 1 minute delay before they can take more pictures, so we can use 1 minute as our threshold.

###Before you begin

In order to run this code, you will need to have the following in place:

* A folder with a set of images (and only images) in it.
* A csv file made using *exiftool* that has date/time metadata from all of the photos in the folder


###Step 1
Set up the workspace
```{r}
rm(list = ls())
library(dplyr)
library(readr)
library(lubridate)
```
###Step 2

First identify the folder containing the images and create a variable that is the list of file names. 

```{r}
filepath<- ("/Users/ebar/Dropbox/R/Zooniverse_work/Small batch")#may have to redirect to wherever the pictures are stored.


#filepath<-("/Volumes/External Drive/Dropbox/R/Zooniverse_work/Small batch") #from mac pro

files<-list.files(filepath) #creates variable files as list of filenames
```
###Step 3 
Now we need to pull in the image metadata.  It was generated and saved as a .csv outside of R using a tool called *exiftool* that is run from the command line.  We should see if we can get *exiftool* installed on the HPC. It works to run exiftool within R (library(exiftool)), but it is VERY VERY SLOW. 

```{r}

#library(readr) if not called at top of code
Meta <- read.csv("~/Dropbox/Zooniverse_work/Kate/R1B2.csv") #obvioulsly, put correct file name here

```

###Step 4
Now that we have the metadata, we can see that the DateTimeOriginal column came in as a factor.  Let's change it with lubridate.  Note that then a very important step is to ORDER the data frame in terms of date/time.  If you fail to order the data frame, when you compare dates/times you will get incorrect output.

```{r}
#library(lubridate)if not called at top of code 
Meta$DateTimeOriginal<-ymd_hms(Meta$DateTimeOriginal)
Meta<-Meta[order(Meta$DateTimeOriginal, Meta$FileName),]#THIS IS KEY
```
###Step 5
Need to filter by camera.  First make new camera number variable.

```{r}
#first make Fielname a chr var
Meta$FileName<-as.character(Meta$FileName)
Meta$cam_num<-substr(Meta$FileName, 1, 5)
cams<-unique(Meta$cam_num)
```

Subset the DFs so we can run the loop and combine each camera to one manifest csv file
```{r}
tempDF1<- filter(Meta, cam_num == cams[1])
tempDF2<- filter(Meta, cam_num == cams[2])
tempDF3<- filter(Meta, cam_num == cams[3])
tempDF4<- filter(Meta, cam_num == cams[4])
tempDF5<- filter(Meta, cam_num == cams[5])
tempDF6<- filter(Meta, cam_num == cams[6])
tempDF7<- filter(Meta, cam_num == cams[7])
```


Next, create a loop to filter and process by camera

```{r}
for (i in 1:length(cams)){
     #subset the DF
     tempDF<-filter(Meta, cam_num == cams[i])
     tempDF
  
     #now we have the subset; need to process using old code
     #Now see if we can calculate the time differences among the photos
     MyDiffs<-diff(tempDF$DateTimeOriginal)#returns what looks like an empty variable in the environment window
     MyDiffs<-as.numeric(MyDiffs) #now it shows up as numeric data
     #Now let's see if we can assign images to events using this logic.  We will need to set the time threshold (default is 1 minute).
}
     thresh<-5 #set a threshold for number of seconds between events
ev<-vector()

     for(i in 1:length(tempDF$DateTimeOriginal)){
          interval<-diff(tempDF$DateTimeOriginal)

          
          ev<-1; Event_num<-numeric() #created new var called ev and set to 1, created empty numeric vector called Event_num. Event_num will store the assigned event for each image
        }
     cond<- interval > thresh #sets condition for assigning to a new event where minutes corresponds to thresh
        
        for(i in 1:(length(tempDF$DateTimeOriginal)-1)){
           if(!cond[i]) ev<-ev else ev<-ev+1
           Event_num<-c(Event_num,ev)

       Event<-c(1,Event_num)
       
       tempDF$Event<-Event
newDF<-rbind(tempDF, tempDF[[i]])
}
       #need a if...else statement to add data from i>= 2 to DF
   
 #rbind(tempDF, tempDF[i])}
         #merge(tempDF,tempDF[i]) #tempDF[i]$Event<-last(tempDF$Event)+1
          # tempDF$Event<-Event else tempDF<-merge.data.frame(tempDF$cam_num)
     # if(i == 1) tempDF$Event<-Event else for (i in 1:(length(cams)){
      #  tempDF<-full_join(tempDF,tempDF$cam_num)
 

  #write.csv(tempDF,"~/Dropbox/Zooniverse_work/Kate/Images_by_event.csv")

#last(tempDF$Event)

```










```{r}
MyDiffs<-diff(Meta$DateTimeOriginal)#returns what looks like an empty variable in the environment window
MyDiffs<-as.numeric(MyDiffs) #now it shows up as numeric data

#Optional: now see if we can convert seconds to minutes, minutes to hours, hours to days
#MyDiffs_Minutes<-MyDiffs/60
#MyDiffs_Hours<-MyDiffs_Minutes/60
#MyDiffs_Days<-MyDiffs_Hours/24

#MyDiffs_Minutes
```
###Step 5 
This seems to be working!  

```{r}
thresh<-60 #set a threshold for number of seconds between events
ev<-vector()
L <- length(Meta$DateTimeOriginal)

for(i in 1:length(Meta$DateTimeOriginal)){
     interval<-diff(Meta$DateTimeOriginal)
     #now convert to minutes
     
     ev<-1; Event_num<-numeric() #created new var called ev and set to 1, created empty numeric vector called Event_num. Event_num will store the assigned event for each image
   }
cond<- interval > thresh #sets condition for assigning to a new event where minutes corresponds to thresh
   
   for(i in 1:(L-1)){
      if(!cond[i]) ev<-ev else ev<-ev+1
      Event_num<-c(Event_num,ev)
  }
  Event<-c(1,Event_num)
  

```
Now append the Event to the data frame csv to capture the event assignment for each image.
```{R}
Meta$Event<-Event
```
###Step 6
Now export Meta for use in assigning images to "image numbers" in the zooniverse manifest style
```{r}
write.csv(Meta, "Images_by_event.csv")
```

###NOTE
This does not work because it sorts by date and time, not by date and time per forest.

  