---
title: "Image Pre-processing 1: Assign images to events"
output: html_notebook
---
##Introduction
This is the R code needed to use the metadata from a folder of images to compare the image time stamps and group images into their respective "events."

An event is a set of pictures taken within a time threshold.  We set our cameras to take up to 3 pictures in a bout, and set them with a 1 minute delay before they can take more pictures, so we can use 1 minute as our threshold.

###Before you begin

In order to run this code, you will need to have the following in place:

* A folder with a set of images (and only images) in it.
* A csv file made using *exiftool* that has date/time metadata from all of the photos in the folder


###Step 1
Set up the workspace
```{r}
rm(list = ls())
library(dplyr)
library(readr)
library(lubridate)
```
###Step 2

First identify the folder containing the images and create a variable that is the list of file names. 

```{r}
filepath<- ("/Users/ebar/Dropbox/R/Zooniverse_work/Small batch")#may have to redirect to wherever the pictures are stored.


#filepath<-("/Volumes/External Drive/Dropbox/R/Zooniverse_work/Small batch") #from mac pro

files<-list.files(filepath) #creates variable files as list of filenames
```
###Step 3 
Now we need to pull in the image metadata.  It was generated and saved as a .csv outside of R using a tool called *exiftool* that is run from the command line.  We should see if we can get *exiftool* installed on the HPC. It works to run exiftool within R (library(exiftool)), but it is VERY VERY SLOW. 

```{r}

#library(readr) if not called at top of code
Meta <- read.csv("~/Dropbox/Zooniverse_work/Kate/manifest_R2.csv") #obvioulsly, put correct file name here

#For Round 3 Data
Meta<-read.csv("~/Dropbox/Zooniverse_work/Kate/manifest_R3.csv")

#For Round 3 Individually Identify Data
Meta<- read.csv("~/Dropbox/Zooniverse_work/Kate/Manifest_R3_Individual_ID.csv")

#For Round 4 Data Individually Identify
Meta<- read.csv("~/Dropbox/Zooniverse_work/Kate/Manifest_R4_Individual_ID.csv")

#For Round 4 Data
Meta<- read.csv("~/Dropbox/Zooniverse_work/Kate/Manifest_R4.csv")
```

###Step 4
Now that we have the metadata, we can see that the DateTimeOriginal column came in as a factor.  Let's change it with lubridate.  Note that then a very important step is to ORDER the data frame in terms of date/time.  If you fail to order the data frame, when you compare dates/times you will get incorrect output.

```{r}
#library(lubridate)if not called at top of code 
Meta$DateTimeOriginal<-ymd_hms(Meta$DateTimeOriginal)
Meta<-Meta[order(Meta$DateTimeOriginal),]#THIS IS KEY
```
Now see if we can calculate the time differences among the photos

```{r}
MyDiffs<-diff(Meta$DateTimeOriginal)#returns what looks like an empty variable in the environment window
MyDiffs<-as.numeric(MyDiffs) #now it shows up as numeric data

#Optional: now see if we can convert seconds to minutes, minutes to hours, hours to days
#MyDiffs_Minutes<-MyDiffs/60
#MyDiffs_Hours<-MyDiffs_Minutes/60
#MyDiffs_Days<-MyDiffs_Hours/24

#MyDiffs_Minutes
```
###Step 5 
This seems to be working!  Now let's see if we can assign images to events using this logic.  We will need to set the time threshold (default is 1 minute).

```{r}
thresh<-60 #set a threshold for number of seconds between events
ev<-vector()
Meta1<- na.omit(Meta)
L <- length(Meta1$DateTimeOriginal)
i<- length(Meta1$DateTimeOriginal)

for(i in 1:length(Meta1$DateTimeOriginal)){
     interval<-diff(Meta1$DateTimeOriginal)
     #now convert to minutes
     
     ev<-1; Event_num<-numeric() #created new var called ev and set to 1, created empty numeric vector called Event_num. Event_num will store the assigned event for each image
   }
cond<- interval > thresh #sets condition for assigning to a new event where minutes corresponds to thresh
   
   for(i in 1:(L-1)){
      if(!cond[i]) ev<-ev else ev<-ev+1
      Event_num<-c(Event_num,ev)
  }
  Event<-c(1,Event_num)
  
unique(cond)
```
Now append the Event to the data frame csv to capture the event assignment for each image.
```{R}
Meta1$Event<-Event
```
###Step 6
Now export Meta for use in assigning images to "image numbers" in the zooniverse manifest style
```{r}
write.csv(Meta1, "Images_by_event_R2.csv")
write.csv(Meta1, "Images_by_event_R3.csv")
write.csv(Meta1, "Images_by_event_R3Individual.csv")
write.csv(Meta1, "Images_by_event_R4Individual.csv")
write.csv(Meta1, "Images_by_event_R4.csv")
```



  