---
title: "Counting contributors"
author: "Erika Barthelmess"
date: "11/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is code to count the number of contributors and identify the top contributors by week from a data set

Set up the work space
```{r}
rm(list = ls())
library(ggplot2)
library(dplyr)
library(readr)
library(lubridate)
```
Now pull in the data set

```{r}
#DF <- read_csv("/Volumes/External Drive/Dropbox/1Courses/ResearchGroup/2019-2020/Learning R/north-country-wild-classifications.10.31.2019.csv")

library(readr)
DF <- read_csv("~/Dropbox/R/NoCoWild/Data/north-country-wild-classifications (2).csv")
```
Now identify the workflows by first making workflow number a factor
```{r}
DF$workflow_id<-as.factor(DF$workflow_id)
workflows<-levels(DF$workflow_id)
```
We want to now isolate to the second (current) workflow:

```{r}
DF2<-filter(DF, workflow_id == 12161)
```
Now let's get to the proper (most recent) workflow version from DF2
```{r}
DF2$workflow_version<-as.factor(DF2$workflow_version)
levels(DF2$workflow_version)


```
So let's just get the classifications from workflow version 6.5
```{r}
DF3<-filter(DF2, workflow_version == 6.5)
#could ask this to automatically choose the latest workflow version
```
Now let's sort out the users by making user name a factor and determining the levels of the factor
```{r}
DF3$user_name<-as.factor(DF3$user_name)
levels(DF3$user_name)
```
Now lets group all the not logged in to the same id
```{r}
library(stringr)
pattern<-"not-logged-in"
replacement<-"not_logged_in"
DF3$user_name<-str_replace_all(DF3$user_name,pattern,replacement)
```


Now let's set the dates as dates
```{r}
library(lubridate)
DF3$created_at<-ymd_hms(DF3$created_at)
#need to convert to ymd for simplicity but not sure how

```
Now let's summarize by user, using dplyr summarize
```{r}
UserEffort<-DF3 %>% group_by(user_name) %>% summarize(
     NumClass = length(classification_id)
)
```
And now let's try to break it down by week
```{r}
start_date<-min(DF3$created_at)
stop_date<-max(DF3$created_at)
period<-interval(start_date, stop_date)
midpoint<-ymd_hms("2019-10-22 12:00:00")
```
How many days is that?
```{r}
num_days<-period/ddays()
```
Now break down by week
61 days divided by 7 days per week = 8.7 weeks
```{r}
week1<-ymd("2019-10-22")
week2<- week1+7
week3<-week2+7
week4<-week3+7
week5<-week4+7
week6<-week5+7
week7<-week6+7
week8<-week7+7


DF3$week <- 1
set<- which (DF3$created_at > week1 &DF3$created_at<week2)
DF3$week[set]<-2

set<- which (DF3$created_at > week2 &DF3$created_at<week3)
DF3$week[set]<-3

```
Last chunk of code not working.  Need to identify those dates past the midpoint and assign them to week 2.  See forest ecology mid term project for ideas.


How many observations per week?
```{r}
Num_obs_perweek<-DF3 %>% group_by(week) %>% summarize(
     Obs = length(classification_id)
)
```

