---
title: "Counting contributors 2"
author: "Erika Barthelmess"
date: "12/18/2019"
output: html_document
---

## Introduction

This is code to count the number of contributors and identify the top contributors by week from a data set

Set up the work space
```{r}
rm(list = ls())
library(ggplot2)
library(dplyr)
library(readr)
library(lubridate)
```
Now pull in the data set

```{r}
#DF <- read_csv("/Volumes/External Drive/Dropbox/1Courses/ResearchGroup/2019-2020/Learning R/north-country-wild-classifications.10.31.2019.csv")

library(readr)
DF <- read_csv("~/Dropbox/R/NoCoWild/Data/north-country-wild-classifications.1.27.2020.csv")
```
Now identify the workflows by first making workflow number a factor
```{r}
DF$workflow_id<-as.factor(DF$workflow_id)
workflows<-levels(DF$workflow_id)
```
We want to now isolate to the second (current) workflow:

```{r}
DF2<-filter(DF, workflow_id == 12161)
```
Now let's get to the proper (most recent) workflow version from DF2
```{r}
DF2$workflow_version<-as.factor(DF2$workflow_version)
versions<-levels(DF2$workflow_version)


```
So let's just get the classifications from workflow version 6.5
```{r}
DF3<-filter(DF2, workflow_version == tail(versions,1))
#automatically chooses the latest workflow version
```
Now let's sort out the users by making user name a factor and determining the levels of the factor.Will do so by creating a new variable.
```{r}
DF3$userFactor<-as.factor(DF3$user_name)
levels(DF3$userFactor)
```
Now lets group all the not logged in to the same id
```{r}
library(stringr)

pattern<-"not-logged-in"
replacement<-grep("not-logged-in",DF3$user_name)
#identifies all rows with user name including not logged
#in

#now reassign factor name
DF3$user_name[replacement]<- "Not logged in"


```
Now there are a couple other names that need to be grouped. Erika_Barthelmess with barthelmess;
```{r}
change<- which(DF3$user_name == "barthelmess" |DF3$user_name=="Erika_Barthelmess")

#And fix
DF3$user_name[change]<-"Erika Barthelmess"
#and now use to replace userFactor
DF3$userFactor<-as.factor(DF3$user_name)
levels(DF3$userFactor)
```


Now let's set the dates as dates
```{r}
library(lubridate)
DF3$created_at<-ymd_hms(DF3$created_at)


```
Now let's assign each day to a week of the year
```{r}
DF3$week<-isoweek(DF3$created_at)
#and change to factor
DF3$weekFactor<- as.factor(as.numeric(DF3$week))
levels(DF3$weekFactor)
```


Now let's summarize by user, using dplyr summarize
```{r}
UserEffort<-DF3 %>% group_by(userFactor) %>% summarize(
     NumClass = length(classification_id)
)
```
And now let's try to break it down by week
```{r}
UserByWeek<-DF3 %>% group_by(week,userFactor) %>% summarise(
     NumClass = length(classification_id)
)

```
Works to this point.  Now let's plot.
```{r}
ggplot(UserByWeek, aes(week, NumClass, group = userFactor))+
     geom_col()
```


Now let's add the date of the last day of the week, with week ending on a Sunday.  Here are some ideas

```{r}
DF3$endDay<-strptime(paste(year(DF3$created_at),DF3$week,7), format = "%Y %U %u")
```
And now breakdown by week but keep end date
```{r}
DF3$endDayFactor<-as.factor(DF3$endDay)
UserByWeek<-DF3 %>% group_by(endDayFactor,userFactor, week) %>% summarise(
     NumClass = length(classification_id),
     
)

```
Looks good.  
Now let's filter by week and max classifications per week to get final product.  Try `top_n` from dplyr.

```{r}
MainContributers<-UserByWeek %>% group_by(week) %>% top_n(4,NumClass)
```
Now let's plot:
Start by getting an actual date for start date
```{r}
MainContributers<-mutate(MainContributers,
       Day = ymd(endDayFactor))
```
Now extract just 2020 data
```{r}
MainContributers<-filter(MainContributers, Day > "2019-12-31")
```

```{r}
ggplot(MainContributers, aes(Day, NumClass, fill = userFactor))+
     geom_col(position = "dodge")+
     facet_wrap(~endDayFactor)
```

