---
title: "Chapter 5 Steps"
output: html_notebook
---

The purpose of this R Notebook is to work through the steps in Chapter 5 from the Wild.ID people. I will be using their original code to determine the purpose for each step and in what format the input and output are. This will tell us how we need to generate our data from Zooniverse to be able to run through their functions.

First, clear the environment, install the packages, and source the script 'TEAM library 1.7.R' This contains the necessary functions. Make sure you set the right working directory. Supporting materials came from the book's publishing page.
```{r}
rm(list=ls())

library(readr)
library(dplyr)
library(tidyr)
library(chron) #works with chronological objects like dates and times
library(reshape) #restructures and aggregates data in a flexible way
library(vegan) #ecological analysis
library(plotrix) #visualize circular data
library(ggplot2) #producing graphics
library(maptools) #produce maps using GIS layers

#Needed to run this in the console. Also needed to change directories in the console.
source("TEAM library 1.7.R")

```

#Load their data
```{r}
team_data<- read.csv(file= "/Users/kateandy/Dropbox/Zooniverse_work/Kate/Chapter_5_Steps/Chapter_5/teamexample.csv", sep= ",", stringsAsFactors=F)
```

#Add taxonomic attributes 
(Class, Order, Family), sourced from IUCN database (.csv file found in appendix 5.5)
```{r}
iucn.full<- read.csv ("/Users/kateandy/Dropbox/Zooniverse_work/Kate/Chapter_5_Steps/Chapter_5/IUCN.csv", sep =",", h=T)

iucn<- iucn.full[, c("Class", "Order", "Family", "Genus", "Species")]
team<- merge(iucn, team_data, all.y=T) 
```

#Run function that elaborates raw data 
Creates 19 column data frame, dates in correct format, creates two new time objects, ID for each photo, and binomial name of species (bin)
```{r}
data<- fix.dta(team)
```

#Check Data
```{r}
#Check headings
names(data)

#Extract first year (2009) and mammals only 
yr2009<- data[data$Sampling.Event == "2009.01" & data$Class == "MAMMALIA",]

#List unique binomial names
unique(yr2009$bin)

#Remove humans from the list
data<- droplevels(data[data$bin!= "Homo sapiens",])

#Check number of camera traps 
unique(yr2009$Sampling.Unit.Name)
#Shows 58 camera traps deployed 

#Check start and end dates
unique(yr2009$Camera.Start.Date.and.Time)
#comes in format yy-mm-dd hh:mm:ss

```

#Derive Sampling Effort
```{r}
#Create table with list of cameras, start and end dates, and number of days camera traps worked

camera_days<-cam.days(data, 2009.01)
#This is similar to the Cam_Trap_Days output I made in cleaning_dataKA.Rmd

#Write table as .txt file
write.table(camera_days, file= "camera_days_2009.txt", quote=F, sep="\t")

#Derive minimum, maximum, median and quartiles of dates and sampling effort
summary(camera_days[,2:4])

```

#Calculate events for each species and camera trap. 
Run threshold for 1 hour (thresh=60) and 1 day (thresh=1440)
```{r}
events_hh<- event.sp(dtaframe=data, year=2009.01, thresh=60) #This generates a table with number of species detected per camera hourly. 
events_dd<- event.sp(dtaframe=data, year= 2009.01, thresh=1440) #This generates a table with the number of species detected per camera daily. This is similar to the table Donovan generated.

#Write the results to the previous step in a .txt file
write.table(events_hh, file="events_hh.txt", quote=F, sep="\t")
write.table(events_dd, file="events_dd.txt", quote=F, sep="\t")


#Write summary table
events_hh_sepcies<- colSums(events_hh)
write.table(events_hh, file="events_hh_species.txt", quote=F, sep="\t")
events_hh_sepcies
#The number of detections for some of the species are off by a few in this table compared to the table in the chapter. Not sure where the source of the error is. Could be a difference in original data I'm using.

events_dd_sepcies<- colSums(events_dd)
write.table(events_dd, file="events_dd_species.txt", quote=F, sep="\t")
events_dd_sepcies
```

#Calculate RAI_hh and RAI_dd
Can do this step in Excel: divide events by sampling effort and multiply by 100 because most values are <0

#Calculate Na誰ve Occupancy 
Na誰ve Occupancy- proportion of camera trap stations where the species has been captured relative to the total number of camera stations sampled.
Can indicate distribution of species 
Not true occupancy measurement- more where species is more or less likely to be detected

We need to calculate the number of camera trap sites where events are greater than zero and divide the value by 58 (the total number of camera trap sites)

function 'f.matrix.creator' makes a table for each species with cameras on rows and days on columns 

function 'naive' yields na誰ve occupancy values for each species
```{r}
mat<-f.matrix.creator(yr2009)
naive_occu_2009<-naive(mat)
write.table(naive_occu_2009, file="naive_occu_2009.txt", sep="\t", quote=F, row.names=F)
#Output is a two column table with species and na誰ve occupancy (for each species) as a decimal. If multiply by 100, can get percentage of camera trap stations where species was detected

```

#Calculate Species Accumulation
```{r}
accumulation<-acc.curve(data, 2009.01)
write.table(accumulation, file="accsp_2009.txt", quote=F, sep="\t")
#Error here, something is going wrong in their function. Can step through piece by piece with their subfunctions, but cannot run code straight through.

```

Next Steps: manipulate our data set from Zooniverse to replicate the set-up from Wild.ID. This will allow us to run through the code easily. 
