---
title: "Chapter 5 Zooniverse Modifications"
output: html_notebook
---

The goal of this R Notebook is to reorder the data frame we get from Zooniverse to match the format from Wild.ID. This will allow us to use the functions from Chapter 5 to calculate naïve occupancy, RAI, and species accumulation.

Load necessary packages and clear the environment
```{r}
rm(list=ls())

library(dplyr)
library(tidyr)
library(readr)
library(lubridate)
library(chron) #works with chronological objects like dates and times
library(reshape) #restructures and aggregates data in a flexible way
library(vegan) #ecological analysis
library(plotrix) #visualize circular data
library(ggplot2) #producing graphics
library(maptools) #produce maps using GIS layers
```

Now load the latest version of the data frame. This was modified from a previous R Notebook called 'cleaning_dataKA.Rmd'. The file is called 'ImageDates2.csv'
```{r}
DF <- read.csv("~/Dropbox/Zooniverse_work/Gus.csv")
```

There are unnecessary columns in this data frame, so let's remove those. 
```{r}
DF1<-subset(DF, select= c("Image1","DateTimeOriginal","Camera_Trap_Days", "Date_Out", "Date_Checked","choice"))
```

Source functions from Wild.ID chapters in console
```{r}
source("TEAM library 1.7.R")
```

Get DF1 to match format for 'data' in the Wild.ID chapter
```{r}
#Change column headings 
names(DF1)<-c("Sampling.Unit.Name", "td.photo", "ndays", "Start.Date", "End.Date", "bin")
```

Let's try replicating the td.photo column twice and then take away date in one column and time in the other.
```{r}
n<-2
DF2<-cbind(DF1, replicate(n,DF1$td.photo))

```

Correct Dates in DF1
```{r}
DF2$Start.Date<- ymd(DF2$Start.Date)
DF2$End.Date<- ymd(DF2$End.Date)
DF2$td.photo<- ymd_hms(DF2$td.photo)
```

Change column heading to get 'Photo.Date' and 'Photo.Time'
```{r}
names(DF2)<-c("Sampling.Unit.Name", "td.photo", "ndays", "Start.Date", "End.Date", "bin", "Photo.Date", "Photo.Time")
```

Get rid of dates from 'Photo.Time' and times from 'Photo.Date'
```{r}
#Gets rid of time from 'Photo.Date'
DF2$Photo.Date<- ymd_hms(DF2$Photo.Date)
DF2$Photo.Date<-as.Date(DF2$Photo.Date, format = "%y/%m/%d")

#Gets rid of date from 'Photo.Time'
DF2$Photo.Time<- ymd_hms(DF2$Photo.Time)
DF2$Photo.Time<- strftime(DF2$Photo.Time, format = "%H:%M:%S")
#Puts in time that is 5 hours behind the td.photo time. Perhaps need to account for time zone. 
```


Add sampling year column because Wild.ID requires it
```{r}
list<- DF2
Sampling.Event<- rep("2019.01", length(DF2$Sampling.Unit.Name))
DF3<-cbind(list,Sampling.Event)
```


Calculate events per species and camera trap
Run threshold for 1 day (thresh=1440)
```{r}
#Need to load the plyr function for this to work. Was getting an error before that said all arguments must be named.
library(plyr)
events_dd<- event.sp(dtaframe=DF3, year= 2019.01, thresh=1440)

#Problem with td.photo first few dates and Start.Date. First photo captured before deployment date. May need to look into how I merged the image dates. Could also be a problem with the camera. 
```


event.sp <- function(dtaframe, year, thresh) {
    # thresh= minutes
    require(reshape)
    hr <- f.separate.events(dtaframe, thresh)
    sel <- subset(hr, select = c(Sampling.Event, Sampling.Unit.Name, Photo.Date, bin, grp))
    del <- unique(sel)
    dta <- rename(del, c(bin = "value"))
    yrsel <- dta[dta$Sampling.Event == year, ]
    events <- cast(yrsel, Sampling.Unit.Name ~ value, length)
}



#I changed the function in here to say DF3 instead of data, but I don't think this will impact future tests if we use the original function.
f.separate.events<-function(DF3,thresh){
	
	#e.data<-by(DF3$td.photo,DF3$Sampling.Unit.Name,f.separate,thresh)
  indx<-which(is.na(DF3$td.photo))
  if(length(indx)>0)
    data<-DF3[-indx,]
  e.data<-f.separate(DF3$td.photo,thresh)
#e.data<-data.frame(grp=unlist(e.data))
data.frame(DF3,grp=paste(DF3$Sampling.Event,".",DF3$Sampling.Unit.Name,".",e.data,sep=""))

	}


f.separate<-function(data,thresh){
	
	#diff(data$td.photo)
	l<-length(data)
	interval<-diff(data)#abs(c(data[2:l],NA)-data)
	interval<-interval*1440 #convert to minutes
	interval<-as.numeric(interval)
  ev<-1;res<-numeric()
	cond<-interval>thresh #about 5 minutes in between events
	for(i in 1:(l-1)){
		if(!cond[i]) ev<-ev
		else ev<-ev+1
		res<-c(res,ev)
		
		}
	c(1,res)
	}

Write Summary Table
```{r}
events_dd_sepcies<- colSums(events_dd)
events_dd_sepcies
```

Naïve Occupancy
```{r}
mat<-f.matrix.creator(DF3)
naive_occu_2019<-naive(mat)
```

Species Accumulation
```{r}
accumulation<-acc.curve(DF3, 2019.01)

#This worked!!
```

Plot Species Accumulation Curve
```{r}
ggplot(accumulation, aes(x=Camera.trap.days, y=species)) +
     geom_line(aes(y=species-sd), colour = "grey50", linetype= "dotted")+
     geom_line(aes(y=species+sd), colour = "grey50", linetype= "dotted")+
     geom_line()

```

Calculate Species Activity
```{r}
activity_24h<- events.hours(DF3)

```


